\documentclass[12pt,twoside]{report}
\usepackage[utf8]{inputenc}

\usepackage[a4paper,width=150mm,top=25mm,bottom=25mm]{geometry}

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{color}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsthm,amssymb,amsmath}
% \usepackage{multirow} % for tables
 \usepackage[english,british]{babel}
 \usepackage{textcomp}
%\usepackage{graphicx}
\usepackage{subfig}
\usepackage{hyperref}
\newtheorem{lemma}{Lemma}
\newtheorem*{remark}{Remark}


\usepackage[table,usenames,dvipsnames]{xcolor}

\usepackage{tikz}
%\usepackage{multirow}
\usetikzlibrary{shapes,arrows}
\usepackage{pdflscape}
\usepackage{rotating}

\usepackage{geometry}
 

\usepackage{xr-hyper} 
%\usepackage[colorlinks=true, pagebackref=true]{hyperref}

\RequirePackage{color}
\newcommand\red[1]{\textcolor{red}{#1}}
\newcommand\blue[1]{\textcolor{blue}{#1}}
\newcommand\green[1]{{\bf\textcolor{ForestGreen}{#1}}}
\definecolor{orange}{rgb}{0.7,0.3,0}
\newcommand\orange[1]{\textcolor{orange}{#1}}
\newcommand\mycol[1]{\textcolor{orange}{#1}}

\usepackage{longtable}
\setcounter{secnumdepth}{5}

\usepackage{fancyhdr}
%\pagestyle{fancy}


\input{Cover/oficialTitle.tex}


\begin{document}
\MakeUGthesePDG    %% très important pour générer la couvérture de thèse



\chapter*{Abstract}
The phenotype of every known living organism is determined mainly by the complicated interactions between the proteins produced in this organism. Understanding
the orchestration of the organismal responses to the external or internal stimuli is based on the understanding of the interactions of individual proteins
and their complexes structures. The prediction of a complex of two or more proteins is the problem of the protein-protein docking field. Docking algorithms 
usually have two major steps: exhaustive 6D rigid-body search followed by the scoring. In this work we made contribution to both of these steps. 
We developed a novel algorithm for 6D exhaustive search, HermiteFit. It is based on Hermite decomposition of 3D functions into the Hermite basis. 
We implemented this algorithm in the program for fitting low-resolution electron density maps. We showed that it outperforms existing algorithms 
in terms of time-per-point while maintaining the same output model accuracy. We also developed a novel approach to computation of a scoring function, 
which is based on simple logical arguments and avoids an ambiguous com- putation of the reference state. We compared it to the existing scoring functions 
on the widely used protein-protein docking benchmarks. Finally, we developed an approach to include water-protein interactions into the scoring functions 
and val- idated our method during the Critical Assessement of Protein Interactions round 47. 

\chapter*{Dedication}
To my parents.

\chapter*{Acknowledgements}
I would like to thank my supervisor Valentin Gordely and co-supervisor Sergey Grudinin for their guidance during my thesis. I also thank my parents, brother and all the people
I was lucky to work with for their support.

\listoffigures 
\newpage
\listoftables
\newpage

\tableofcontents


\newpage
\chapter{Introduction}

  \section{Role of proteins and their interactions in the cell}
  \input{Intro/RoleOfPPInteractions.tex}
  
  \newpage
  
  \section{Experimental methods to probe protein-protein interactions}
  \input{Intro/MethodsExperimental.tex}
  
  \newpage
  
  \section{Computational methods to probe protein-protein interactions}
  \input{Intro/MethodsComputational.tex}
  
  \newpage
  
  \section{Aim of work}
  \input{Intro/Aim.tex}
   
\newpage
\chapter{Hermite fitting}

  \section{Introduction}
  \input{Hermite/Introduction.tex}

  \newpage
  
  \section{Methods}
  \input{Hermite/Methods.tex}

  \newpage
  
  \section{Analysis}
  \input{Hermite/Analysis.tex}
  
  \newpage
  
  \section{Results and Discussion}
  \input{Hermite/Results.tex}

  \newpage
  
\chapter{Scoring functions for protein-protein docking}

  \section{Introduction}
  \input{Scoring/Introduction.tex}
  
  \newpage
  
  \section{Methods}
  \input{Scoring/Methods.tex}
  
  \newpage

  \section{Results and Discussion}
  \input{Scoring/Results.tex}

  \newpage
  
\chapter{Conclusion and outlook}
\input{Conclusion.tex}

\appendix
\chapter{Dual optimization problem}
\label{Ch:appendixDual}
\input{Scoring/AppendixDual}
\chapter{Sequential minimal optimization algorithm}
\label{Ch:AppendixSMO}
\input{Scoring/AppendixSMO}
\chapter{Docking benchmarks results}
\input{Scoring/tables/zdockTexTableCompareHomologs}
\input{Scoring/tables/rosettaTexTableCompHomologs}


  
\bibliographystyle{plain}
\bibliography{Intro/Citations/IntroCitations.bib,Bibliography/CitationsHermite.bib,Bibliography/CitationsScoring.bib,Bibliography/WaterBibliography.bib}

\end{document}